The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with \textit{Gaia} Data and Beyond

### 2019-05-08 paper/ms.tex
Remove mentions of toy

The fiducial coordinate system for these toy simulations is the rest frame of
the aligned toy galaxy at the beginning of the simulation.

@@

\begin{figure*}[htb!]
\begin{center}
\includegraphics[width=342.078286667pt]{fig/midplane_fit_chervinsim.pdf}
\end{center}
\caption{The local midplane determined at the fiducial Solar radius
($8.2\,\kpc$) for 4 different time steps from toy simulations
of a Sagittarius encounter with the Milky Way \citep{2018MNRAS.481..286L}. As
before, we have subtracted the best fit $A\sin{(\phi+B)}+C$ curve to account
for inaccuracies in the galactocentric coordinate system. Error bars are
calculated as in Figure~\ref{fig:midplane}. (\Gus{Check:}) The upper
panels show the midplane as a function of azimuth before the first encounter
near the Solar circle at $t=2.0\,\Gyr$ and $t=4.0\,\Gyr$. As later encounters occur which bring the
Sagittarius-like object closer to the Solar circle, we can see that stronger
midplane variations result. In fact, one can see that an $m=2$ mode is excited
in the lower left panel at $t=6.0\,\Gyr$ --- this is consistent with Figure~17 of
\citet{2018MNRAS.481..286L}, which shows that an $m=2$ mode is excited (note
that $m=0$ and $m=1$ modes are stronger, but these are removed in our
sine-curve subtraction). The fact that the $t=6.9\,\Gyr$ panel looks
qualitatively similar to the panels from the FIRE simulations
(Figure~\ref{fig:midplane}) is evidence that the midplane variations are
produced in part by mergers.}
\label{fig:midplane_chervin}
\end{figure*}

@@

We compute the same midplane variation in Figure~\ref{fig:midplane_chervin},
but for four succcessive timesteps of the toy simulation of a Sagittarius encounter
\citep{2018MNRAS.481..286L}. Again we have subtracted a best fit curve of the
form $\text{A} \sin{\left(\phi + \text{B}\right)} + \text{C}$, with the values
for $\text{A}$ being $9.5$, $2.5$, $-212$, and $-394\,\pc$, for $\text{B}$
being $0.0013$, $0.0007$, $-0.63$, and $-1.00\,\text{rad}$ and $\text{C}$
being $2.6$, $-7.8$, $-65$, and $-53\,\pc$ chronologically for each of the four timesteps shown.

>>>>

The fiducial coordinate system for these N-body simulations is the rest frame of
the aligned host galaxy at the beginning of the simulation.

@@

\begin{figure*}[htb!]
\begin{center}
\includegraphics[width=342.078286667pt]{fig/midplane_fit_chervinsim.pdf}
\end{center}
\caption{The local midplane determined at the fiducial Solar radius
($8.2\,\kpc$) for 4 different time steps from live N-body simulations
of a Sagittarius encounter with the Milky Way \citep{2018MNRAS.481..286L}. As
before, we have subtracted the best fit $A\sin{(\phi+B)}+C$ curve to account
for inaccuracies in the galactocentric coordinate system. Error bars are
calculated as in Figure~\ref{fig:midplane}. (\Gus{Check:}) The upper
panels show the midplane as a function of azimuth before the first encounter
near the Solar circle at $t=2.0\,\Gyr$ and $t=4.0\,\Gyr$. As later encounters occur which bring the
Sagittarius-like object closer to the Solar circle, we can see that stronger
midplane variations result. In fact, one can see that an $m=2$ mode is excited
in the lower left panel at $t=6.0\,\Gyr$ --- this is consistent with Figure~17 of
\citet{2018MNRAS.481..286L}, which shows that an $m=2$ mode is excited (note
that $m=0$ and $m=1$ modes are stronger, but these are removed in our
sine-curve subtraction). The fact that the $t=6.9\,\Gyr$ panel looks
qualitatively similar to the panels from the FIRE simulations
(Figure~\ref{fig:midplane}) is evidence that the midplane variations are
produced in part by mergers.}
\label{fig:midplane_chervin}
\end{figure*}

@@

We compute the same midplane variation in Figure~\ref{fig:midplane_chervin},
but for four succcessive timesteps of the live N-body simulation of a Sagittarius encounter
\citep{2018MNRAS.481..286L}. Again we have subtracted a best fit curve of the
form $\text{A} \sin{\left(\phi + \text{B}\right)} + \text{C}$, with the values
for $\text{A}$ being $9.5$, $2.5$, $-212$, and $-394\,\pc$, for $\text{B}$
being $0.0013$, $0.0007$, $-0.63$, and $-1.00\,\text{rad}$ and $\text{C}$
being $2.6$, $-7.8$, $-65$, and $-53\,\pc$ chronologically for each of the four timesteps shown.
